---
title: "Class 12: Structural Bioinformatics pt.1"
author: "Alex Weitzel"
date: "2/13/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## PDB statistics

Here w inspect the types of structures in the main database for 3D biomolecular data - the PDB.

https://www.rcsb.org/

https://www.rcsb.org/stats/summary
^^csv from here^^

> Q1: Download a CSV file from the PDB site (accessible from “Analyze” -> “PDB Statistics” >
“by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project
and determine the percentage of structures solved by X-Ray and Electron Microscopy. 

```{r}
# read in file
stats <- read.csv("Data Export Summary.csv", row.names = 1)

#calculate precentage values asked for
#stats["X-Ray",]$Proteins / sum(stats$Total)
#stats["Electron Microscopy",]$Proteins / sum(stats$Total)

ans <- stats$Total / sum(stats$Total) * 100
names(ans) <- rownames(stats)
round(ans,2)

```


> Q2: Also can you determine what proportion of structures are protein? Aim to have a rendered GitHub
document with working code that yields your answers.

> Q3: Type HIV in the PDB website search box on the home page and determine how many
HIV-1 protease structures are in the current PDB?








